The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-12-27 r_r/letter_to_reviewers.Rmd
submitted r&r mofogit add .git add .
trying to create word file

---
#title: "Response to Editors and Reviewers"
#author: "ozan"
date: "`r Sys.Date()`"
output: pdf_document
bibliography: ./../other/burd_recruiting_chapter.bib
csl: ./../other/apa.csl
---

@@

XXXX X, 2023

>>>>

---
#title: "Response to Editors and Reviewers"
#author: "ozan"
#date: "`r Sys.Date()`"
#output: pdf_document
output: word_document
bibliography: ./../other/burd_recruiting_chapter.bib
csl: ./../other/apa.csl
---

@@

December 20, 2023

### 2023-12-27 r_r/manuscript_rihe_r_r.Rmd
trying to create word file

---
title: "The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities"
#author: 
#  - Ozan Jaquette
#  - Crystal Han
#  - Irma Castañeda
bibliography: ./../other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
    toc: FALSE
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
csl: ./../other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \usepackage{setspace}
      - \usepackage{fancyhdr}
      - \usepackage{titlesec}
      #- \doublespacing
      - \floatsetup{capposition=top}
      - \newcommand{\beginsupplement}{
      - \setcounter{table}{0}  
      - \renewcommand{\thetable}{S\arabic{table}} 
      - \setcounter{figure}{0} 
      - \renewcommand{\thefigure}{S\arabic{figure}}}
fontsize: 12pt
---

>>>>

---
title: "The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities"
#author: 
#  - Ozan Jaquette
#  - Crystal Han
#  - Irma Castañeda
bibliography: ./../other/burd_recruiting_chapter.bib
output:
  #bookdown::word_document2:
  bookdown::pdf_document2:
    toc: FALSE
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    keep_tex: true
csl: ./../other/apa.csl
urlcolor: blue
#always_allow_html: true
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \usepackage{setspace}
      - \usepackage{fancyhdr}
      - \usepackage{titlesec}
      #- \doublespacing
      - \floatsetup{capposition=top}
      - \newcommand{\beginsupplement}{
      - \setcounter{table}{0}  
      - \renewcommand{\thetable}{S\arabic{table}} 
      - \setcounter{figure}{0} 
      - \renewcommand{\thefigure}{S\arabic{figure}}}
fontsize: 12pt
---
